Deep mutational scanning of hemagglutinin helps distinguish the evolutionary fate of human H3N2 influenza virus lineages

### 2018-01-01 paper/manuscript.tex
Reword fig 1 caption

\title{Deep mutational scanning of hemagglutinin helps distinguish the evolutionary fate of human H3N2 influenza virus}

@@

\begin{figure}
\centerline{\includegraphics[width=\textwidth]{figs/dms_overview/dms_overview.pdf}}
\caption{\label{fig:dms_overview}
{\bf Deep mutational scanning experiments of H3 HA.}
(A) We generated Perth/2009 HA mutant virus libraries in MDCK-SIAT1-TMPRSS2 cells using a helper virus approach described in~\cite{doud2016accurate}.
We then passaged the initially generated pool of mutant viruses at low MOI to establish a genotype-phenotype linkage and select for functional HA variants. 
Deep sequencing of the variants before and after selection allowed us to infer the H3 site-specific amino-acid preferences.
(B) The DMS experiments were completed in biological triplicate, starting from independent preps of the wildtype HA genes to create the mutant plasmids. 
In addition, we passaged and deep sequenced library 3 in technical replicate, denoted 3-1 and 3-2, to estimate the experimental noise within a single biological replicate.
(C) Mutation frequencies of nonsynonymous, stop, and synonymous mutations for the mutant DNA, mutant virus, and unmutated DNA and virus controls. 
There is selection against nonsynonymous and stop codons in the mutant viruses. 
The percentages signify the frequency of stop codons remaining in the passaged mutant viruses relative to their starting frequency in the mutant plasmid libraries after correcting for the stop codon frequencies in the wildtype DNA and viruses.
(D) The Pearson correlations for the amino-acid preferences between each pair of replicates are shown. 
The correlation between the technical replicates is comparable to that between biological replicates, indicating that the low MOI passage contributes to much of the experimental noise. 
}
\end{figure}

>>>>

\title{Deep mutational scanning of hemagglutinin helps distinguish the evolutionary fate of human H3N2 influenza virus lineages}

@@

\begin{figure}
\centerline{\includegraphics[width=\textwidth]{figs/dms_overview/dms_overview.pdf}}
\caption{\label{fig:dms_overview}
{\bf Deep mutational scanning experiments of H3 HA.}
(A) We generated Perth/2009 HA mutant virus libraries using a helper virus approach described in~\cite{doud2016accurate}.
We then passaged this pool of mutant viruses at low MOI to establish a genotype-phenotype linkage and to select for functional HA variants. 
Deep sequencing of the variants before and after selection allowed us to infer the H3 site-specific amino-acid preferences.
(B) The DMS experiments were performed in biological triplicate, starting from independent preps of the wildtype HA genes to create the mutant plasmids. 
We also passaged and deep sequenced library 3 in technical replicate, denoted 3-1 and 3-2, to estimate the experimental noise within a biological replicate.
(C) Mutation frequencies of nonsynonymous, stop, and synonymous mutations for the mutant DNA, mutant virus, and unmutated DNA and virus controls. 
There is selection against nonsynonymous and stop codons in the mutant viruses. 
(D) The Pearson correlations for the amino-acid preferences between each pair of replicates are shown. 
The correlation between the technical replicates is comparable to that between biological replicates, indicating that much of the experimental noise comes from passaging at low MOI. 
}
\end{figure}
